---
title: "Lab 07 - Modelling course evaluations"
author: "Mate Roka"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
evals %>% 
  ggplot(aes(x=score))+
  geom_density()
evals %>% 
  summarise(mean=mean(score),median=median(score))
```

*The distribution is slightly negatively skewed, which is also shown by the mean and median not coinciding with the mode. This mostly matches my expectations as I would think most students dont score courses very drastically.*

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
evals %>% 
  ggplot(aes(y=score, x=bty_avg))+
  geom_point()
evals %>% 
  ggplot(aes(x=bty_avg, y=score))+
  geom_jitter()
```

*Jitter adds a random small amount of variance to the value of the variables, breaking up their structured appearance caused by the fact that students can only rate with one decimal accuracy.*

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

*score = 3.88 + 0.067bty_avg*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit}
evals %>% 
  ggplot(aes(x=bty_avg, y=score))+
  geom_jitter()+
  geom_smooth(method = lm, se=FALSE)
```

3. Interpret the slope of the linear model in context of the data.

*For every point the average beauty rating increases by, the score increases by 0.067 points*

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*The intercept means that a professor with an average beauty rating of 0 would have a score of 3.88. While this could happen, it is highly unlikely that someone would have an average beauty rating of 0.*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$r.squared
```

*Add your interpretation here*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(score_bty_aug, aes(x=.fitted, y=.resid)) + 
  geom_jitter()+
  geom_hline(yintercept = 0, lty="dashed")
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
evals %>% 
  ggplot(aes(x=rank))+
  geom_bar()
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model
score_rank_fit <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(score ~ rank, data=evals)
# tidy model output
tidy(score_rank_fit)
```

**

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model
score_gender_fit <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(score ~ gender, data=evals)
# tidy model output
tidy(score_gender_fit)
```

```{r score_gender_intercept}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

Intercept is `r round(score_gender_intercept, 2)`, 
Slope is `r round(score_gender_slope, 2)`

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model
score_bty_gender_fit <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(score ~ bty_avg + gender, data=evals)
# tidy model output
tidy(score_bty_gender_fit)
```

*Add your narrative here.*

```{r }
evals %>% 
ggplot(aes(x=bty_avg, y=score, colour = gender)) +
  geom_jitter()
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
